Reasoning about the rigor of perl programs: \\ \large gaps, limits to understanding, and means to ameliorate

### 2024-05-21 sciperl/paper.tex
sectioned out

\documentclass[twoside]{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
     colorlinks=true,
     allcolors=NavyBlue
}
\usepackage{listings}
\lstset{language=Perl}

@@

From this two things are clear:

1. rigorous testing of any individual \textit{instruction} within a stack over it's expected domain of inputs, and a sampling of data outside of that is valuable.
2. The interaction of an instruction with its immediate follower and predecessor must also be well understood; these multi-instruction sections can indeed be treated as though they are themselves more complicated instructions.

This is the actual theoretical underpinning behind the two testing concepts we are all familiar with (unit and integration testing), but most don't think too hard about.
It's this lack of concrete understanding that leads to frequent confusion and ineffective testsuites the world over.

@@

a. Devel::Cover does not quite cover the subject

@@

b. But I've got 100% coverage, now what?

@@

c. eval {} is not enough

@@

d. Fitness for a particular purpose

@@

e. Quality with non-functional Characteristics

@@

For example, suppose I have the option of multiple modules on CPAN which I see do roughly the same thing in function X.
It would greatly simplify my decision as to what to use if I already knew ahead of time:

1. What's the bandwidth of this function; how does it perform?
2. How complex is it?  I may have to read and debug this.
3. Is it doing non-portable things?

And so on.

>>>>

\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
     colorlinks=true,
     allcolors=NavyBlue
}
\usepackage{listings}
\lstset{language=Perl}

@@

From this two things are clear:
\begin{itemize}
\item rigorous testing of any individual \textit{instruction} within a stack over it's expected domain of inputs, and a sampling of data outside of that is valuable.
\item The interaction of an instruction with its immediate follower and predecessor must also be well understood; these multi-instruction sections can indeed be treated as though they are themselves more complicated instructions.
\end{itemize}
This is the actual theoretical underpinning behind the two testing concepts we are all familiar with (unit and integration testing), but most don't think too hard about.
It's this lack of concrete understanding that leads to frequent confusion and ineffective testsuites the world over.

@@

\subsection{Devel::Cover does not quite cover the subject}

@@

\subsection{But I've got 100\% coverage, now what?}

@@

\subsection{eval \{\} is not enough}

@@

\subsection{Fitness for a particular purpose}

@@

\subsection{Quality with non-functional Characteristics}

@@

For example, suppose I have the option of multiple modules on CPAN which I see do roughly the same thing in function X.
It would greatly simplify my decision as to what to use if I already knew ahead of time:
\begin{itemize}
\item What's the bandwidth of this function; how does it perform?
\item How complex is it?  I may have to read and debug this.
\item Is it doing non-portable things?
\end{itemize}
And so on.
